Anisotropic in-plane thermal conductivity observed in multilayer silicene

### 2017-06-26 latex/paper.tex
add pre logo

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-06-24 17:55:39
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure files
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,2}$}
\author{Zhi-Xin Guo${}^{3}$}
\author{Shi-you Chen}
\author{Hongjun Xiang}
\author{Xin-Gao Gong${}^{1,2}$}
\email{xggong@fudan.edu.cn}
\affiliation{
${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
${}^2$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China\\
${}^3$Department of Physics, Xiangtan University, Xiangtan 411105, China
}
\begin{abstract}
By means of non-equilibrium molecular dynamics simulation, we systematically study the thermal transportation properties of different types of multilayer silicon. It is found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in thickness direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicon with different reconstruction can reach up to $11.6 W/mK$, and can be as low as $1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure. This work could be helpful in the field of heat management, thermoelectric applications involving silicon and other multilayer nano materials in the future.
\begin{description}
\item[Keywords]
Thermal conductivity, multilayer silicon, surface reconstruction, anisotropy
\end{description}
\end{abstract}

@@

\begin{table*}
\caption{\label{tab:table1}
Symmetry of the structures, binding energy $E_c(eV/Si)$ and structure features}
\begin{ruledtabular}
\begin{tabular}{cccccccc}
 Name
 &Minimal period
 &Symmetry
 &$E_c$ in Guo
 &$E_c$ in MD
 &Buckling Feature\\
\hline
2l1 & $1 \times 1$ & Cmme & 5.000 &4.145 &Smooth \\
2l2 & $\sqrt{2}\times\sqrt{2}$ & C12/m1 & 4.991 & 4.204 & Large buckling and symmetric\\
2l3 & $2 \times 2$ & C12/m1 & 5.063 & 4.257 & Large buckling and tilt symmetric\\
2lh & $2 \times 2$ & P1 & 5.073 & 4.216 & Large buckling\\
2lr3 & $\sqrt{3}\times\sqrt{3}$ & P1 & - & 4.225 & Small buckling and symmetric\\
3l1 & $2 \times 1$ & P121/m1 & 5.138 & 4.337 & -\\
3l2 & $2 \times 1$ & P1 & 5.135 & 4.298 & -\\
4l1 & $2 \times 1$ & P1 & 5.225 & 4.368 & -\\
2l2 &$\sqrt{2}\times\sqrt{2}$ & C12/m1 & 4.991 & 4.204 & Large buckling and symmetric\\
2l3 & $2 \times 2$ & C12/m1 & 5.063 & 4.257 & Large buckling and tilt symmetric\\
2lh & $2 \times 2$ & P1 & 5.073 & 4.216 & Large buckling\\
2lr3 & $\sqrt{3}\times\sqrt{3}$ & P1 & - & 4.225 & Small buckling and symmetric\\
3l1 & $2 \times 1$ & P121/m1 & 5.138 & 4.337 & -\\
3l2 & $2 \times 1$ & P1 & 5.135 & 4.298 & -\\
4l1 & $2 \times 1$ & P1 & 5.225 & 4.368 & -\\

\end{tabular}
\end{ruledtabular}
\end{table*}

@@

 &$\kappa_{z,\infty}$
 &$\kappa_{a,\infty}$
 &$\chi$
 &
 &$\kappa_{z,\infty}$
 &$\kappa_{a,\infty}$
 &$\chi$\\
\hline
2l1 & 11.6 & 6.5 & 43.9\% & 2l2 & 1.5 & 1.2 & 20.0\%\\
2l3 & 5.0 & 9.7 & 48.5\% & 2lr3 & 8.2 & 3.5 & 57.3\%\\
2lh & 2.0 & 2.5 & 20.0\% & 3l1 & 11.5 & 2.9 & 74.8\%\\
3l2 & 10.2 & 5.2 & 49.0\% & 4l1 & 10.2 & 3.4 & 66.7\%\\
5l1 & 11.7 & 5.7 & 51.3\% & 6l1 & 10.3 & 7.8 & 24.3\%\\
8l1 & 13.2 & 14.9 & 11.4\% & 10l1 & 13.3 & 13.5 & 1.5\%\\
Si111 & 33.6 & 34.7 & 3.2\% & Silicene & 11.4 & 11.6 & 1.7\%\\

\end{tabular}
\end{ruledtabular}
\end{table*}

>>>>

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-06-26 15:07:24
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,2}$}
\author{Chao-Yu Chen${}^{3}$}
\author{Zhi-Xin Guo${}^{3}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen}
\author{Hong-Jun Xiang}
\author{Xin-Gao Gong${}^{1,2}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China\\
  ${}^3$Department of Physics, Xiangtan University, Xiangtan 411105, China
}
\begin{abstract}
  By means of non-equilibrium molecular dynamics simulation, we systematically study the thermal transportation properties of different types of multilayer silicon. It is found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in thickness direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicon with different reconstruction can reach up to $11.6 W/mK$, and can be as low as $1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure. This work could be helpful in the field of heat management, thermoelectric applications involving silicon and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicon, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

\begin{table*}
  \caption{\label{tab:table1}
    Symmetry of the structures, binding energy $E_c(eV/Si)$ and structure features}
  \begin{ruledtabular}
    \begin{tabular}{cccccccc}
      Name
           & Minimal period
           & Symmetry
           & $E_c$ in Guo
           & $E_c$ in MD
           & Buckling Feature                                                                       \\
      \hline
      2l1  & $1 \times 1$             & Cmme    & 5.000 & 4.145 & Smooth                            \\
      2l2  & $\sqrt{2}\times\sqrt{2}$ & C12/m1  & 4.991 & 4.204 & Large buckling and symmetric      \\
      2l3  & $2 \times 2$             & C12/m1  & 5.063 & 4.257 & Large buckling and tilt symmetric \\
      2lh  & $2 \times 2$             & P1      & 5.073 & 4.216 & Large buckling                    \\
      2lr3 & $\sqrt{3}\times\sqrt{3}$ & P1      & -     & 4.225 & Small buckling and symmetric      \\
      3l1  & $2 \times 1$             & P121/m1 & 5.138 & 4.337 & -                                 \\
      3l2  & $2 \times 1$             & P1      & 5.135 & 4.298 & -                                 \\
      4l1  & $2 \times 1$             & P1      & 5.225 & 4.368 & -                                 \\
      2l2  & $\sqrt{2}\times\sqrt{2}$ & C12/m1  & 4.991 & 4.204 & Large buckling and symmetric      \\
      2l3  & $2 \times 2$             & C12/m1  & 5.063 & 4.257 & Large buckling and tilt symmetric \\
      2lh  & $2 \times 2$             & P1      & 5.073 & 4.216 & Large buckling                    \\
      2lr3 & $\sqrt{3}\times\sqrt{3}$ & P1      & -     & 4.225 & Small buckling and symmetric      \\
      3l1  & $2 \times 1$             & P121/m1 & 5.138 & 4.337 & -                                 \\
      3l2  & $2 \times 1$             & P1      & 5.135 & 4.298 & -                                 \\
      4l1  & $2 \times 1$             & P1      & 5.225 & 4.368 & -                                 \\
    \end{tabular}
  \end{ruledtabular}
\end{table*}

@@

            & $\kappa_{z,\infty}$
            & $\kappa_{a,\infty}$
            & $\chi$
            &
            & $\kappa_{z,\infty}$
            & $\kappa_{a,\infty}$
            & $\chi$                                                                \\
      \hline
      2l1   & 11.6                & 6.5  & 43.9\% & 2l2      & 1.5  & 1.2  & 20.0\% \\
      2l3   & 5.0                 & 9.7  & 48.5\% & 2lr3     & 8.2  & 3.5  & 57.3\% \\
      2lh   & 2.0                 & 2.5  & 20.0\% & 3l1      & 11.5 & 2.9  & 74.8\% \\
      3l2   & 10.2                & 5.2  & 49.0\% & 4l1      & 10.2 & 3.4  & 66.7\% \\
      5l1   & 11.7                & 5.7  & 51.3\% & 6l1      & 10.3 & 7.8  & 24.3\% \\
      8l1   & 13.2                & 14.9 & 11.4\% & 10l1     & 13.3 & 13.5 & 1.5\%  \\
      Si111 & 33.6                & 34.7 & 3.2\%  & Silicene & 11.4 & 11.6 & 1.7\%  \\
    \end{tabular}
  \end{ruledtabular}
\end{table*}
